---
title: "Aides Tests"
author: "Eric McDaniel"
date: "Dec 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

#Methods

# RESULTS

#Graphical Results/South Carolina
##Male
```{r}
ScarolinaM <- filter(Scarolina, sex== "M")
barchartGC(~infected + group, data=ScarolinaM, type="percent", main="South Carolina Male")
```

##Female
```{r}
ScarolinaF <- filter(Scarolina,sex=="F")
barchartGC(~infected + group, data=ScarolinaF, type="percent", main="South Carolina Female")
```
#Both

```{r}
barchartGC(~infected+group,data=Scarolina, type ="percent", main= "South Carolina Male and Females")
```

#Graphical Results/Central Africa
##Male
```{r}
cenAfricaM <- filter(cenAfrica,sex=="M") 
barchartGC(~infected + group, data=cenAfricaM, type="percent", main="Central Africa Male")
```

##Female
```{r}
cenAfricaF <- filter(cenAfrica,sex=="F") 
barchartGC(~infected + group, data=cenAfricaF, type="percent", main="Central Africa Female")
```
##Both
```{r}
barchartGC(~infected+group,data=cenAfrica, type ="percent", main= "Central Africa Male and Females")
```


#Graphical Results/Korea
##Male
```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~infected + group, data=koreaM, type="percent",  main="Korea Male")
```

##Female
```{r}
koreaF <- filter(korea,sex=="F")
barchartGC(~infected + group, data=koreaF, type="percent", main="Korea Female")
```

##Both
```{r}
barchartGC(~infected+group,data=korea, type ="percent", main= "Korea Male and Females")
```

#Numerical Results/South Carolina
##Male
```{r}
ScarolinaM_table <- xtabs(~infected + group, data = ScarolinaM)
rowPerc(ScarolinaM_table)
```
##Female
```{r}
ScarolinaF_table <- xtabs(~infected + group, data = ScarolinaF)
rowPerc(ScarolinaF_table)
```
##Both
```{r}
Scarolina_table <- xtabs(~infected + group, data = Scarolina)
rowPerc(Scarolina_table)
```

#Numerical Results/Central Africa
##Male
```{r}
cenAfricaM_table <- xtabs(~infected + group, data = cenAfricaM)
rowPerc(cenAfricaM_table)
```

##Female
```{r}
cenAfricaF_table <- xtabs(~infected + group, data = cenAfricaF)
rowPerc(cenAfricaF_table)
```

##Both
```{r}
cenAfrica_table <- xtabs(~infected + group, data = cenAfrica)
rowPerc(cenAfrica_table)
```

#Numerical Results/Korea
##Male
```{r}
koreaM_table <- xtabs(~infected + group, data = koreaM)
rowPerc(koreaM_table)
```

##Female
```{r}
koreaF_table <- xtabs(~infected + group, data = koreaF)
rowPerc(koreaF_table)
```
#Both
```{r}
korea_table <- xtabs(~infected + group, data= korea)
rowPerc(korea_table)
```



#Inferential Results/South Carolina
#Male
```{r}
chisqtestGC(ScarolinaM_table)
```
#Female
```{r}
chisqtestGC(ScarolinaF_table)
```
#Both
```{r}
chisqtestGC(Scarolina_table)
```


#Inferential Results/Central Africa
#Male
```{r}
chisqtestGC(cenAfricaM_table)
```

#Female
```{r}
chisqtestGC(cenAfricaF_table)
```

#Both
```{r}
chisqtestGC(cenAfrica_table)
```


#Inferential Results/Korea
#Male
```{r}
chisqtestGC(koreaM_table)
```

#Female
```{r}
chisqtestGC(koreaF_table)
```

#Both
```{r}
chisqtestGC(korea_table)
```


# Conclusion





